### 2019-07-01 README.Rmd
changed formula formatting

$Formula 1:$

  $$P = 1-\sum_{i=0}^{k-1} \frac{\binom{m}{i}\binom{N-M}{n-i}}{\binom{N}{n}}$$

>>>>

Formula 1:

$$ P = 1-\sum_{i=0}^{k-1} \frac{ \binom{m} {i} \binom{N-M} {n-i} } {\binom{N} {n} } $$

where N is the total number of genes in the background, M is the number of genes within that background that also in the gene set of interest, n is the size of the list of genes of interest and k is the number of genes within that are in the background. The background by default is all the genes that have annotation.
